---
title: "Package Related Functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Package-Related}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(utilitarian)
```

## usePackage  

Don't know if something is installed? Want your code to install packages when run if they're absent? `usePackage` is here to help!

```{r usePackage}

usePackage("dichromat")

```

Combine `usePackage()` with the `purrr` package to attempt to attach and (install if unavailable) multiple packages. 
Walk doesn't return an output, only the secondary effects. In this case, an attached package from each of those in the character vector.
```{r usePackage2}
purrr::walk(c("DT", "dplyr", "lubridate", "readr", "ggplot2", "ggridges", "viridis", "hrbrthemes", "forcats", "tidyr"), ~ usePackage(.x))
```



## libraries  

Tired of quoting and typing in multiple library statements? No more!

### Several flavours:  

#### Silent and easy typing  

Don't bother with quotes. Just type your package names in and off you go. 

```{r libraries1}
libraries(dichromat, jsonlite)
sessionInfo()
```

#### Quoted  

Like `library()` but better.

```{r libraries2}
libraries("dichromat", "jsonlite", quoted = T)
sessionInfo()
```

#### Quoted in a Character Vector  

Like `library()` but *even* better.

```{r libraries3}
mypkgs <- c("dichromat", "jsonlite")
libraries(mypkgs, quoted = T)
sessionInfo()
```

#### Unquote or Quoted but with Verbose Feedback  

Because you like R to talk back. 

```{r libraries4}
libraries(dichromat, verbose = TRUE)
```

